---
title: "Fuel Efficiency Forensics: A Comparative Regression Analysis of 1974 Automobile Data"
author: "David Namgung"
date: "02/08/2026"
output: 
  html_document:
    theme: cerulean        # "flatly" (modern), "journal" (classic), "cosmo" (clean)
    highlight:      # "tango" (subtle), "zenburn" (dark code blocks)
    toc: true            
    toc_float:           # Makes the TOC float on the left as you scroll
      collapsed: true   
      smooth_scroll: true 
    number_sections: true
    code_folding: show   
    df_print: paged        
latex_engine: xelatex
---

<style>
@import url('https://fonts.googleapis.com/css2?family=Fira+Code:wght@400;500&family=Lato:wght@400;700&display=swap');

/* 1. MAIN FONT (Lato) */
body, h1, h2, h3, h4, p, li {
    font-family: 'Lato', sans-serif !important;
}

/* 2. CODE FONT (Fira Code) */
pre, code, .sourceCode {
    font-family: 'Fira Code', monospace !important;
    font-size: 14px;
}

/* 3. TITLE BLOCK BANNER SIMULATION */
/* This creates the "title-block-banner: true" look manually */
#header {
    background: linear-gradient(135deg, #2c3e50, #4ca1af); /* Dark Blue/Green Gradient */
    color: white;
    padding: 40px;
    border-radius: 0 0 10px 10px;
    margin-bottom: 30px;
    text-align: center;
}
#header h1.title {
    color: white;
    font-weight: 900;
    font-size: 3em;
}
#header h4.author, #header h4.date, #header h3.subtitle {
    color: #ecf0f1;
}

/* 4. TABLE OF CONTENTS DESIGN */
.list-group-item.active, .list-group-item.active:focus, .list-group-item.active:hover {
    background-color: #2c3e50;
    border-color: #2c3e50;
}

/* 5. SMOOTH SCROLLING ADJUSTMENT */
html {
    scroll-behavior: smooth;
}
</style>

## Context

<div class="alert alert-info">
Identifying the key engineering factors driving fuel efficiency in 1974 automobiles and build a robust predictive model for Miles Per Gallon (MPG).
</div>

Using the **1974 Motor Trend US magazine dataset**, this project investigates the relationship between **gasoline mileage ($y$)** and two specific design features: **engine displacement ($x_1$)** and the **number of carburetor barrels ($x_6$)**[cite: 27].


#### Key Findings

* **Engine Displacement is King:** Statistical analysis confirms a strong, negative linear relationship between engine size and fuel efficiency. 
As displacement increases, MPG drops significantly ($p < 0.001$).

* **The "More is Less" Paradox:** While the number of carburetors ($x_6$) appears to correlate with lower mileage, 
our analysis reveals it is **statistically insignificant** ($p > 0.05$) when engine size is already accounted for.

* **Model Selection:** We compared four candidate models using **5-Fold Cross-Validation** and **BIC (Bayesian Information Criterion)**.
    * While the "Full Model" (Displacement + Carburetors) offered the lowest raw prediction error, the "Reduced Model" (Displacement Only) provided a superior balance of simplicity and accuracy.

* **Predictive Power:** Our final selected model explains approximately **77% of the variance** in fuel efficiency ($R^2_{adj} \approx 0.77$).

---

## Data Initialization

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
library(gridExtra)
library(tidyverse)
library(knitr)
library(dplyr)

file1 <- paste0("https://raw.githubusercontent.com/",
                "mcgillstat/regression/main/data/data-table-B3.csv")
data_table_B3 <- read.csv(file = file1)
```

## Analysis

### Regression Modelling and Significance

We fit a multiple linear regression model relating gasoline mileage y (miles per gallon) 
to engine displacement x1 and the number of carburetor barrels x6.

We constructed the analysis-of-variance table, tested for significance of regression and defined appropriate hypotheses for this test. 

$$y = \beta_0 + \beta_1 x_1 + \beta_6 x_6 + \epsilon$$

```{r}
dat <- data.frame(
  y = data_table_B3$y, # $y$ = Miles/gallon
  x1 = data_table_B3$x1, # $x_1$ = Displacement
  x6 = data_table_B3$x6 # $x_6$ = Carburetor
)

# Multiple linear regression model:
# y = \beta_0 + \beta_1 x1 + \beta_6 x6 + epsilon

model_1 <- lm(y ~ x1 + x6, data = dat)
summary(model_1)

# Generate ANOVA table
anova(model_1)
```

For the significance of regression, we want 
to summarize the conclusions via the overall fit, using the 
F-statistic result from the summary of the overall model.

#### Hypotheses:

Neither predictors have any linear relationship with gasoline milage.
$$H_0: \beta_1 = \beta_6 = 0$$


At least 1 predictor is useful for predeciting gasoline mileage.
$$H_1: \text{ At least one } \beta_j != 0$$



**Test Statistic:**

"F-statistic: 53.67 on 2 and 29 DF, p-value: 1.79e-10", from fitting the model, 
where F = MSR/MSRes = (SSR/(p-1))  /  (SSRes)/(n-p)).

F = MSR/MSRes = (974.31/(3-1)) / (263.23)/(32-3)) = approximately 53.65,
where p = 3 and n = 32.

Since p-value 1.79e-10 is much smaller than $\alpha$ = 0.05, we reject the null hypothesis $H_0$.


#### Interpretation:

There is a statistically significant linear relationship between gasoline mileage ($y$) and the combination of engine displacement ($x_1$) and carburetor barrels ($x_6$).


### Miles per Gallon versus Engine Displacement
```{r}
ggplot(dat, aes(x = x1, y = y)) +
  geom_point(aes(color = as.factor(x6)), size = 3) +
  geom_smooth(method = "lm", color = "black", linetype = "dashed") +
  labs(title = "MPG vs. Engine Displacement",
       subtitle = "Colored by Number of Carburetors",
       x = "Engine Displacement (cu. in.)",
       y = "Miles Per Gallon (MPG)",
       color = "Carburetors") +
  theme_minimal()
```

### $R^2$ and adjusted $R^2$ of this model

Comparing the $R^2$ and adjusted $R^2$ to the simple linear regression model relating to mileage $y$ to engine displacement $x_1$. This will tell us how well the model explains the data compared to the simpler model.

Recall: $R^2$ is the proportion of variance in the response variable that is predictable from the independent variables.


```{r}
# Extract metrics from the Multiple Linear Regression (MLR) model
r2_mlr <- summary(model_1)$r.squared # 0.7872928
adj_r2_mlr <- summary(model_1)$adj.r.squared # 0.7726233

# Fit the Simple Linear Regression model (y ~ x1)
model_slr <- lm(y ~ x1, data = dat)
summary(model_slr)

# Extract metrics from the SLR model
r2_slr <- summary(model_slr)$r.squared # 0.7722712
adj_r2_slr <- summary(model_slr)$adj.r.squared # 0.7646803

# Multiple Linear Regression Model
cat("R-Squared for MLR: ", r2_mlr, "\n")
cat("Adjusted R-Squared for MLR: ", adj_r2_mlr, "\n")

# Simple Linear Regression Model
cat("R-Squared for SLR: ", r2_slr, "\n")
cat("Adjusted R-Squared for SLR: ", adj_r2_slr)
```

#### Results:
**Multiple Linear Regression ($x_1 + x_6$) :**

* $R^2$ of MLR: 0.7872928
* Adjusted $R^2$ of MLR: 0.7726233

**Simple Linear Regression ($x_1$ only) :**

  * $R^2$ of SLR: 0.7722712 
  * Adjusted $R^2$ of SLR: 0.7646803


$R^2$ always increases or stays the same when we add more variables 

Coefficient of Determination $R^2$ measures the proportion of variance in the response ($y$) explained by the predictors. $R^2$ = 1 - $SS_{Res} / SS_{T}$

Adjusted $R^2$ penalizes the model for adding unnecessary predictors. 

It accounts for the degrees of freedom (n-p), Adjusted $R^2$ = 1 - $(SS_{Res}/(n-p)) / (SS_{T}/(n-1))$


#### Interpretation:

The MLR model ($R^2$ = approx. 78.73%) explains slightly more variation than the SLR model ($R^2$ =  approx. 77.23%).

The adjusted metric $R^2$ also increases from SLR's approx. 76.47%  to MLR's approx. 77.26%.

Thus, adding carburetor barrels ($x_6$) to the model provided a VERY small improvement in fit, but only a tiny amount. Engine displacement ($x_1$) accounts for the vast majority of 
the predictive power.



### Individual Predictor Significance (t-tests)

What the t-test does for us:

```{r}
# Extract coefficients
coef_summary <- summary(model_1)$coefficients
kable(coef_summary, caption = "Regression Coefficients")
```

#### Hypotheses, $\alpha = 0.05$ :

Predictor adds no value to model given all other predictors are already included
$$H0: \beta_j = 0.$$

Predictor is significant.
$$Ha: \beta_j != 0.$$ 


#### Results:

**For $x_1$:**
* t-test = -8.660425
* p-value = 1.549965e-09

Since p = 1.549965e-09 which is smaller than $\alpha$ = 0.05,
we reject the null hypothesis #H_0$: $\beta$j = 0. 

Engine displacement makes a significant contribution to the modeleven when carburetor barrels ($x_6$) are included. There is strongevidence that engine displacement is associated with gasoline mileage.


**For  $x_6$:**
* t-test = 1.431 
* p-value = 1.630948e-01

Since p = 1.630948e-01 > $\alpha$ = 0.05, we FAIL to reject $H_0$.

The number of carburetor barrels does not make a statistically significant contribution to the model GIVEN that engine displacement is already included.


#### Interpretation:

Despite the overall model being significant, only engine displacement is a significant individual predictor. Carburetor barrels appears to be redundant with the presence of engine displacement. 



### Confidence vs. Prediction Intervals

Finding a 95% CI for $\beta_1$.

```{r}
# 95% CI for x1, using confint() for accuracy and simplicity
confint(model_1, "x1", level = 0.95)
```

100(1-$\alpha$) is the confidence interval for regression coefficient $\beta_j$ given by:

$\beta_hat_j$ ± t_(n-p),$\alpha$/2 multiplied by "estimate standard error" or (ese) of $\beta_hat_j$ in our summary:

* $\beta_hat_j$ = -0.05314767
* ese($\beta_hat_j$) = 0.006136843
* Critical value from t-distribution with df n-p = 32 - 3 = 29 
* $\alpha$/2 = 0.025 is approx. 2.045 


#### Result: 
Lower Bound: -0.06569892 
Upper Bound: -0.04059641


#### Interpretation:

We are 95% confident that the true slope for $x_1$ lies between -0.06569957 and -0.04059643

Since the entire interval is negative, we are statistically certain that larger engines are associated with lower gas mileage.

For every 1 cubic inch increase in engine displacement, we estimate the car's fuel efficiency will drop between 0.041 and 0.066 miles per gallon, holding the numbers of carburetors constant. 

 

### t-statistics for predicting gas mileage

t-statistics for: 
* $H_0: \beta_1 = 0$, number of carburetors and engine displacement are redundant.

* $H_0: \beta_6 = 0$, they provide significant predictions for mileage.

We want to test if a coefficient = 0, $t_0 = (beta_hat_j)$ / (ese($beta_hat_j$))

t-distribution with n-p degrees of freedom under $H_0$.

We reject the $H_0$ if |$t_0$| > $t_{(crit(n-p,\alpha / 2))}$

Recall, for $\alpha$ = 0.05 and df = 20, the critical value is approcimately 2.045.

```{r}
# Extracting coefficients table to see t-values
coef_summary <- summary(model_1)$coefficients
coef_summary

# Get specific t-values for x1 and x6
t_beta1 <- coef_summary["x1", "t value"] # [1] -8.660425
t_beta6 <- coef_summary["x6", "t value"] # [1] 1.431084
# Or simply read from coefficients summary table

# degrees of freedom for critical value
df_res <- summary(model_1)$df[2]  # [1] 29

# t-statistic for x1:
cat("T-Statistic for x1: ", t_beta1, "\n") # [1] -8.660425
# t-statistic for x6:
cat("T-Statistic for x6: ", t_beta6, "\n") # [1] 1.431084
# degrees of freedom:
cat("Degrees of Freedom: ", df_res) # [1] 29
```

#### Results:

**Displacement:**

For $\beta_1$ the t-value = |-8.660425| = 8.660425, thus, we reject $H_0$ since 8.660425 > 2.045. 

There is statistically significant evidence that engine displacement contributes to the model.


**Carburetors:**

For $\beta_6$ = |1.431084| = 1.431084, we FAIL to reject $H_0$ since 1.431084 is NOT > 2.045. 


#### Interpretation:

There is statistically **significant evidence** that engine displacement contributes to the model. While there is **insufficient evidence** to claim thatthe number of carburetor barrels contribute significantly to the model when displacement is already included.



### Confidence Interval Example

Finding a 95% Confidence Interval on the mean gasoline mileage when 
* $x_1 = 275$
* $x_6 = 2$

```{r}
# Defining the new observation (mean gasoline milage when x1 = 275, x6 = 2)
new_car <- data.frame(x1 = 275, x6 = 2)

# 95% CI for Mean Response
predict(model_1, newdata = new_car, interval = "confidence", level = 0.95)

# Extract the coefficients table to see beta_hat values
coef_summary <- summary(model_1)$coefficients
```


#### Results:

The point estimate is approx. 20.19 from the equation: 

$$ \hat{y} = \beta_0 - \beta_1(275) + 0.96(2)$$

* Lower bound: 18.97221
* Upper Bound: 21.50257

They measure the uncertainty in the position of the regression plane (the average) at that specific point.


#### Interpretation:

We are 95% confident that **the true average gasoline mileage** for all cars with an engine displacement of 275 cubic inches and 2 carburetor barrels lies between **18.97 and 21.40** Miles per Gallon ($y$), a range of 2.43 MPG.

The small gap suggests that we are very sure about that the average mileage of cars with these specs, would be approx. 20.2 Miles Per Gallon, give or take 1.2 MPG. 



### Prediction Interval Example

Finding a 95% prediction interval for a new observation on gasoline mileage when:
* $x_1 = 275$
* $x_6 = 2$

```{r}
# New car's specs
new_car_data <- data.frame(x1 = 275, x6 = 2)

# 95% Prediction Interval
predict(model_1, newdata = new_car_data, interval = "prediction", level = 0.95)

# Extract the coefficients table to see beta_hat values
coef_summary <- summary(model_1)$coefficients
coef_summary

# Residual Standard Error
sigma_hat <- summary(model_1)$sigma
sigma_hat
df_res <- summary(model_1)$df[2]
df_res
```

#### Results:

**point estimate: 20.18739**
**Lower Bound: 13.8867**
**Upper Bound: 26.48808**


#### Interpretation:

We are 95% confident that a single specific automobile with 275 cubic inches engine displacement and 2 carburetor barrels will have a gasoline mileage **between 13.89 and 26.49** Miles per Gallon, a range of 12.6 MPG.


The large gap in the Prediction Interval compared theConfidence Interval suggests that individual cars arehighly variable. If we buy one specific car, its mileagecould plausibly be as low as 14 or as high as 26 which in itself is a large pool of unit.


While the model is very good at identifying the average behavior,it is **not very precise at predicting individual outcomes** because there is a lot of random variation, $\epsilon$, between cars that engine size alone cannot explain.


### Model Validation and Out-Of-Sample Performance

**Recall:**
$SS_{Res}$ measures the error on the data the model was trained on. The model is optimized specifically to minimize this error, "fitting" itself to the specific noise in that dataset.


$PRESS$ measures the error on data points held out (leave-one-out cross-validation). Because the model hasn't seen these points during fitting, it cannot overfit to them, resulting in larger errors.

$PRESS$ residual for point $i$ is measured by  $e_i$ = $e_i$ / $1-h_ii$.

$e_i$ being the original residual, $h_ii$ is the leverage of $i$ which is always between 0 and 1 (and typically > 0).

Since the denominator is less than 1, the $PRESS$ residual is mathematically guaranteed to be larger in magnitude than the ordinary residual. 

Therefore, the sum of squared $PRESS$ residuals $PRESS$ will be larger than the sum of squared ordinary residuals $SS_{Res}$

We want to find $SS_T$ and the out-of-sample $R^2$ using the given PRESS statistic.



```{r}
model <- lm (model_1)

# Residuals and Leverage (hat values)
hat_vals <- lm.influence(model)$hat
hat_vals

# Residuals
residuals <- resid(model)

# PRESS Residuals, predictively adjusted residuals
pressres <- resid(model)/(1 - lm.influence(model)$hat) 

# SSRes, Residual sum of squares
SSRes <- sum(residuals ^2)
# PRESS, Predicted Residual Error Sum of Squares
PRESS <- sum(pressres ^2)

# Total Sum of Squares, Sum of differences from the mean of y
SST <- sum((dat$y - mean(dat$y))^2)

# Out of sample $R^2$ (Prediction R-Squared)
R2_prediction <- 1 - (PRESS/SST)

# Residual Sum of Squares
cat("Residual Sum of Squares (SSRes): ", SSRes, "\n")
cat("Predicted Residual Error Sum of Squares (PRESS): ", PRESS, "\n")
cat("Total Sum of Squares (SST): ", SST, "\n")
cat("Out-of-sample R-Squared (R2_prediction): ", R2_prediction)
```

#### Results: 

* $R^2$ of MLR: 0.7872928
* Adjusted $R^2$ of MLR: 0.7726233
* Out-of-sample $R^2$: 0.7343405


#### Interpretation:

Based on the out-of-sample $R^2$: 

* Prediction $R^2$ (0.734) is very close to the Adjusted $R^2$ (0.773). This indicates that the model generalizes well and theperformance does not drop much when it faces new cars.

* It is not suffering from severe overfitting.The model is not relying on quirks or outliers in the 32 car dataset to achieve its score.

* We can expect this model to explain about 74% of the variation in gasoline mileage for future cars.

If the Prediction $R^2$ were significantly lower (e.g., 0.50), it would suggest the model fits the training data well but fails to predict new, unseen observations accurately.




### Cross-Validation & Optimal Model Selection

We deleted half the observations (chosen at random), and refit the regression model. 

```{r}
set.seed(123)

# Split
dat
n <- nrow(dat)
train_indexes <- sample(1:n, size = n/2) # Random 16 indexes

train_data <- dat[train_indexes, ]
test_data  <- dat[-train_indexes, ]

# Fit the model on the TRAINING data only
model_half <- lm(y ~ x1 + x6, data = train_data)
# model_half

# Compare Coefficients
cat("Full Model (n=32): ", coef(model_1), "\n")
cat("Half Model (n=16): ", coef(model_half), "\n")

# Out-of-Sample $R^2$ on the TEST data
# Predict y values for the test set using half-model
preds <- predict(model_half, newdata = test_data)

# Sum of Squared Errors (SSE) for the test set
sse_test <- sum((test_data$y - preds)^2)

# Total Sum of Squares (SST) for the test set
sst_test <- sum((test_data$y - mean(test_data$y))^2)

# Calculate R-Squared
r2_out <- 1 - (sse_test / sst_test)

# Predictive Performance
cat("Out-of-Sample R-Squared: ", r2_out) # 0.8234939
```


#### Interpretation:

##### Have the regression coefficients changed dramatically?

In terms of the $\beta_1$, 
**Displacement**:
* Full Model: -0.053
* Half Model: -0.05101

The coefficient for $\beta_1$ remained relatively stable, indicating a robust relationship.

However, 
**Carburetors** ($\beta_6$) changed noticeably from 
* 0.9592231 (full model) to 
* 0.824131 (half model), but it is still not a dramatic change.
  
This confirms that $\beta_6$ is an unstable estimator sensitive to the specific data points used.


##### How well does this model predict?

$$Out-of-Sample R-Squared = 0.8234939$$

In terms of this specific metric, the model appears to predict extremely well—better, than the model trained on the full dataset. 

It explains 82.35% of the variance in the unseen test data. However, this high performance is likely misleading and indicates instability due to the small sample size (n = 16 for training)


We must consider the random 16 cars for testing, which could have lined up perfectly with the trend of the other 16 cars. We must also consider the high variance. A stable model would give consistent results, but one split can give 0.82 while another gives 0.40. Thus, the model performance is heavily dependent on exactly which cars are chose for training. 


While the Out-of-Sample R-Squared of 0.823 suggests excellent predictive power, the fact that it exceeds the full model's fit 0.787 implies this result is an artifact of sampling variability. The small sample size, N = 32, makes the model unstable; its performance fluctuates wildly depending on which observations are included in the training set.



### Computing $R^2$, adjusted $R^2$, $C_p$, AIC and BIC for each model. 

```{r}
# Models
m1 <- lm(y ~ 1, data = dat)
# y = $\beta$0 + $\epsilon$, Intercept only

m2 <- lm(y ~ x1, data = dat)
# y = $$ \beta_0 + \beta_1x1 + \epsilon, x_1 $$ (only Displacement)

m3 <- lm(y ~ x6, data = dat)
# y = $$\beta_0$ + \beta6 x6 + \epsilon, x_6 $$ (only Carburetors)

m4 <- lm(y ~ x1 + x6, data = dat)
# y = $$ \beta_0 + \beta_1 x1 + \beta_6 x6 + \epsilon$$, (Full Model)

# MSE ($\sigma^2$) from the full model for Cp calculation
mse_full <- (summary(m4)$sigma)^2 
mse_full

# Function to calculate all metrics for a single model
get_metrics <- function(model, full_mse) {
  s <- summary(model)
  n <- nrow(dat)
  p <- length(coef(model)) # Number of parameters with intercept
  rss <- sum(resid(model)^2) # Residual Sum of Squares

  # Metrics
  r2 <- s$r.squared
  adj_r2 <- s$adj.r.squared
  aic <- AIC(model)
  bic <- BIC(model)

  # Mallows' $C_p$ Formula: (RSS / MSE_full) - (n - 2*p)
  cp <- (rss / full_mse) - (n - 2 * p)
  return(c(p=p, R2=r2, Adj_R2=adj_r2, Cp=cp, AIC=aic, BIC=bic))
}

# Results
results <- data.frame(
  Model_1 = get_metrics(m1, mse_full),
  Model_2 = get_metrics(m2, mse_full),
  Model_3 = get_metrics(m3, mse_full),
  Model_4 = get_metrics(m4, mse_full)
)
# Transpose
print(t(results))
```

#### Results:

We can first eliminate model 1 because it assumes neither engine size nor carburetors affect gas mileage. It assumes every car simply gets the average mileage, ȳ. 

$R^2$ and Adjusted $R^2$ = 0, and AIC = 211.8 which is the highest score, a.k.a. the worst score. 

We have previously proved that engine size do matter. 

We can then eliminate model 3 because it assumes ONLY the number of carburetors matters while engine size does not. 

$R^2$ = 0.237 means that this model only explains 24% of the difference in gas mileage. Comparing 24% to Models 2 and 4's approx. 76-77%, we can already eliminate Model 3 since it only explains approximate 24% of the difference in gas mileage. AIC is also 205.1139 which is the second highest (worst) score. 

Now between Model 2 and 4:
* In terms of $R^2$ and Adjusted $R^2$, Model 4's is slightly higher. This means that model 4, technically fits the the data better.

* Model 4's AIC is slightly lower, which suggests that its prediction accuracy is a slightly better.

* Model 4's Mallow's $C_p$ is 3.0 which is exactly p (p = 3). This is the definition of a "unbiased" model. Model 2's Mallow's $C_p$ = 3.048003, which is also a good fit since it's approximate 2 and is not < 2. It hits the target despite 1 less variable. 

* The most important metric revolves around BIC. BIC applies a stronger penalty for adding variables and favor the simpler model when the improvement in fit is marginal. 

The lower BIC for Model 2 confirms that the extra variable is unnecessary complexity. Recall, we confirmed the t-test for $x_6$ to be insignificant with p = 0.163 > $\alpha$ (0.05). Adding it barely improves the fit. 

* Model 2 is much simpler with only 1 predictor vs. having the need for 2.


#### Conclusion:

Although Model 4 has a slightly higher Adjusted $R^2$ and lower AIC, the differences are negligible. Model 2 has the lowest BIC (170.8 vs 172.1), which penalizes complexitymore strictly. 

Additionally, the previous t-test showed that x6 is not statistically significant. 

Therefore, Model 2 provides the best balance of fit and simplicity, the better choice that performs just as well as Model 4, but simpler and easier to interpret.




### 5-fold cross-validation error

Identifying the most appropriate model, which has the smallest cross-validation error.

```{r}
set.seed(123)

# Shuffle the dataset randomly
#    We scramble the rows so the folds are random
dat_shuffled <- dat[sample(nrow(dat)), ]

# Create 5 "Folds" (groups)
#    This assigns a number (1, 2, 3, 4, or 5) to every row
folds <- cut(seq(1, nrow(dat_shuffled)), breaks = 5, labels = FALSE)

# Create a generic function to run CV on any model formula
calc_cv_error <- function(formula_input) {
  mse_vector <- numeric(5) # A place to store the 5 errors

  for (i in 1:5) {
    # Define Test and Train for this fold
    testIndices <- which(folds == i, arr.ind = TRUE)
    testData    <- dat_shuffled[testIndices, ]
    trainData   <- dat_shuffled[-testIndices, ]

    # fit the model using lm() on TRAINING data
    model <- lm(formula_input, data = trainData)

    # Predict on TEST data
    preds <- predict(model, newdata = testData)

    # Calculate MSE for this fold: mean((Actual - Predicted)^2)
    mse_vector[i] <- mean((testData$y - preds)^2)
  }
  # Return average of the 5 MSEs
  return (mean(mse_vector))
}

# Run the function for all 4 models
cv_error_1 <- calc_cv_error(y ~ 1)          # Model 1
cv_error_2 <- calc_cv_error(y ~ x1)         # Model 2
cv_error_3 <- calc_cv_error(y ~ x6)         # Model 3
cv_error_4 <- calc_cv_error(y ~ x1 + x6)    # Model 4
cat("CV Error Model 1:", cv_error_1, "\n")
cat("CV Error Model 2:", cv_error_2, "\n")
cat("CV Error Model 3:", cv_error_3, "\n")
cat("CV Error Model 4:", cv_error_4)
```



#### Results and Interpretation:

In terms of the different models, we can already eliminate Model 1 and 3 due to their high error results. Simply using the average and the number of carburetors are weak predictors. 

Based on the 5-fold cross validation, Model 4 is the selected model because it minimizes the estimated test Mean Squared Error and shows the smallest cross-validation error result. 

This suggests that the carburetor variable, while not themost statistically significant in hypothesis testing, likely provides a very small amount of useful signal that improves prediction accuracy on unseen data just enough to outperform the simpler model.

Previously, we preferred Model 2 because BIC and Parsimony favored simplicity, and the difference in fit, $R^2$, was negligible. Model 2 is better for explanation, while Model 4 is slightly better for pure prediction.
